---
title: "MEASURING PSYCHOLOGY"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, warning=FALSE, echo=FALSE}
source(here::here("R", "functions.R"))
```


**Measuring Psychology** is a global community and study group of aspiring and current students, professors, and interested people that help each other. We all have an interest in measurement theory for psychology and psychometrics. Through *discussions*, *solidarity*, and *openness*, we are boosting psychological science by improving measurement.

<div class="headers">
<h1>Join our discussion</h1>
</div>

```{r}
# teste
as_card(group_name = "Reading list",
        event_name = "Here you will find papers suggested by our community and you may add a suggestion yourself.",
        img_src = "images/google_sheets.svg",
        link = 'https://docs.google.com/spreadsheets/d/1VUtka6tC1bZucqsJ-8pvOM78azqjYyrIS4Dt3tCtrdg/edit#gid=0'
        )
```

```{r}
as_card(group_name = "Sign up",
        event_name = "If you want to take part in our live sessions, follow this link to fill the interest form.",
        img_src = "images/google_forms.svg",
        link = 'https://forms.gle/LhhBVLEX5C9Ybnta8'
        )
```

<div class="headers">
<h1>Community</h1>
</div>

We are a group of people who are interested in measurement theory and psychometrics for psychology.

We are from all around the world, with different backgrounds (from undergraduate to Ph.D.'s; from academia and industry).

This is a safe place to learn, ask questions and teach.

<div class="headers">
<h1>Meetings calendar</h1>
</div>

```{r}
toastui::calendar()

```


<div class="headers">
<h1>Join our Slack channel</h1>
</div>

Link to the channel

<div class="headers">
<h1>About us</h1>
</div>

```{r}
plot(hist(mtcars$disp))
```
