---
title: "Measuring Psychology"
output:
  distill::distill_article:
    includes:
      in_header: assets/header.html
      after_body: assets/_footer.html
    css: assets/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, warning=FALSE, echo=FALSE}
source(here::here("R", "functions.R"))
```


Add a description

<div class="headers">
<h1>Join us</h1>
</div>

Testing the cards function

```{r}
# teste
as_card(group_name = "Reading list",
        event_name = "Descricao da planilha",
        img_src = "images/google_sheets.svg",
        link = 'https://docs.google.com/spreadsheets/d/1VUtka6tC1bZucqsJ-8pvOM78azqjYyrIS4Dt3tCtrdg/edit#gid=0'
        )
```

```{r}
as_card(group_name = "Sign up",
        event_name = "Descricao do formulário",
        img_src = "images/google_forms.svg",
        link = 'https://forms.gle/LhhBVLEX5C9Ybnta8'
        )
```

<div class="headers">
<h1>Community</h1>
</div>

We are a group of people who are interested in measurement theory and psychometrics for psychology.

We are from all around the world, with different backgrounds (from undergraduate to Ph.D.'s; from academia and industry).

This is a safe place to learn, ask questions and teach.

<div class="headers">
<h1>Meetings calendar</h1>
</div>

```{r}
toastui::calendar()

```


<div class="headers">
<h1>Join our Slack channel</h1>
</div>

Link to the channel

<div class="headers">
<h1>About us</h1>
</div>

```{r}
plot(hist(mtcars$disp))
```