---
title: "MEASURING PSYCHOLOGY"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, warning=FALSE, echo=FALSE}
source(here::here("R", "functions.R"))
source(here::here("assets", "calendar.R"))
```


**Measuring Psychology** is a global community with 200+ registered members interested in discussions, collaborations, and networking in the field of measurement in the human sciences. We all have an interest in measurement theory for psychology and psychometrics. Our community and study group comprises aspiring and current students, professors, and interested people who help each other. We are boosting psychological science by improving measurement through *discussions*, *solidarity*, and *openness*.

This community has become a hub for academics and researchers. It has helped them learn in group studies and discussions with established researchers, such as Dr. Derek Briggs, Dr. Laura Bringmann, Dr. Markus Eronen, Dr. Elina Vessonen, Dr. Stefanie Morris, Dr. James Grice, and Dr. Vithor Franco.

<div class="headers">
<h1>Join our discussion</h1>
</div>

```{r reading list}
as_card(group_name = "Reading list",
        event_name = "You will find our past and current list of readings. Take a look on what we've been studying.",
        img_src = "images/google_sheets.svg",
        link = 'https://docs.google.com/spreadsheets/d/1SOlgVUkUCKVM9kD9AvtMvqsG6lbsh0Nqj9Kom5eESXw/edit#gid=0'
        )
```

```{r sign up form}
as_card(group_name = "Sign up",
        event_name = "If you want to join our live meetings and Slack community, follow this link to complete the registration form. You will also find a link to subscribe to receive updates by email.",
        img_src = "images/google_forms.svg",
        link = 'https://forms.gle/WbnrzcdxJZ3Gwf9ZA'
        )
```

<div class="headers">
<h1>Community</h1>
</div>

We have a growing community from almost all parts of the world with different backgrounds. For instance, we are: 

  a. both from academia and industry;  
  b. from undergraduate students to Ph.D.s;  
  c. from psychology, education, statistics, mathematics, and many more.
  
We all are interested in improving our area of research by learning and applying measurement theory and psychometrics in our studies. Most importantly, we are an open-arms community built to have a safe environment to study, exchange ideas, and collaborate. Please, consider reading our [code of conduct](coc.html).

In the map below, you'll find the location and affiliation of some of our members.

```{r map, layout="l-screen-inset"}
library(leaflet)
old_map <- readr::read_csv("assets/map_data_fixed.csv")
new_map <- readr::read_csv("assets/map_data_2023.csv") |> # From participants_database.R
  dplyr::rename(c(university = affilliation, 
                  country = country_of_residence))
map_data <- dplyr::bind_rows(old_map, new_map) |> 
  dplyr::with_groups(c(university:longitude), dplyr::mutate, n = dplyr::n())
# calculate center point for setting zoom
bbox <- ggmap::make_bbox(map_data$longitude, map_data$latitude)
lon <- sum(bbox[c(1, 3)]) / 2
lat <- sum(bbox[c(2, 4)]) / 2

map_data %>% 
        leaflet() %>%
        setView(lon, lat, zoom =2) %>% 
        addTiles() %>% 
        addMarkers(lng = ~longitude, lat = ~latitude, 
                popup = paste0(
                '<b>Affiliation:</b> ',map_data$university, '<br>',
                '<b>Participants:</b> ', map_data$n, '<br>'
                ),
                clusterOptions = markerClusterOptions()
        )
```


<div class="headers">
<h1>Meetings calendar</h1>
</div>

- 2023-03-06 - Beyond Statistical Ritual: Theory in Psychological Science.  
- 2023-03-20 - Dr. Liam Satchell: Getting the measurement message out.  
- 2023-04-03 - Dr. Carlos Collares: Applications of Item Response Theory to Psychology.  
- 2023-04-17 - Yago Luksevicius: Ontological diversity in gaming disorder measurement: a nationally representative registered report.  
- 2023-05-01 - Maul, A. (2017). Rethinking traditional methods of survey validation.  
- 2023-05-15 - Dr. James Steele: Can we measure effort in cognitive tasks? Examining the application of Additive Conjoint Measurement and the Rasch model.  
- 2023-05-29 - Dr. Riet van Bork: A causal theory of error scores.  
- 2023-06-12 - Dr. Matthias Borgstede and Dr. Frank Eggert: Squaring the circle: From latent variables to theory-based measurement.  
- 2023-06-26 - Dr. Alexander Christensen:  A Psychometric Network Perspective on the Validity and Validation of Personality Trait Questionnaires  
- 2022-07-10 - Ben Giber: Lord, F. M. (1953). On the statistical treatment of football numbers + Scholten, A. Z., & Borsboom, D. (2009). A reanalysis of Lord’s statistical treatment of football numbers.  
- 2023-07-24 - Claudia Bucheweitz: A comparative contrast of clinimetric and psychometric methods for constructing indexes and rating scales.  
- 2022-08-07 - Felipe Vieira: Schimmack, U. (2021). The validation crisis in psychology.

```{r calendar}
library(toastui)
#library(htmltools)
calendar(view = "month", 
         useDetailPopup = TRUE,
         navigation = TRUE,
         defaultDate = Sys.Date(),
         useNavigation = TRUE,
         startDayOfWeek  = 1, 
        narrowWeekend = TRUE) %>%
  cal_schedules(mp_calendar)

```

Our meetings are recorded, and the videos are shared within the community afterward.


<div class="headers">
<h1>Join our Slack channel</h1>
</div>

Please complete the registration form if you are interested in participating in this community. We'll send an invitation to the Slack workspace for every registered participant.

<div class="headers">
<h1>About us</h1>
</div>


:::::::::::::: {.columns}
::: {.wrap width="50%"}


```{r }
desc_rafael <- "Rafael Bastos is a Master's student in Psychology in the field of construction, validation, and standardization of instruments at São Francisco University (Brazil). Works mainly on the following subjects: psychometrics, statistics, and quantitative methods."

profile_card(img_src = "images/rafael.jpg", name = "Rafael Bastos", title="Founder and Administrator", 
             description = desc_rafael, 
             email="mailto:rafavsbastos@gmail.com",
             website="https://rafavsbastos.medium.com/",
             twitter="https://twitter.com/rafavsbastos",
             linkedin="https://www.linkedin.com/in/rafael-valdece-sousa-bastos/")

``` 

:::
::: {.wrap width="50%"}

```{r }
desc_marwin <- "Marwin Carmo is a Master's student in Psychiatry at University of São Paulo (Brazil). Interested in:
sleep medicine, psychometrics, quantitative methods, open science, and R programming."

profile_card(img_src = "images/marwin.jpg", name = "Marwin Carmo", title = "Founder and Administrator",
             description = desc_marwin, 
             email="mailto:marwin@usp.br",
             website="https://marwincarmo.github.io/",
             twitter="https://twitter.com/marwincarmo",
             linkedin="https://www.linkedin.com/in/marwin-carmo/")
``` 

:::
::::::::::::::

