---
title: "MEASURING PSYCHOLOGY"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, warning=FALSE, echo=FALSE}
source(here::here("R", "functions.R"))
```


**Measuring Psychology** is a global community and study group of aspiring and current students, professors, and interested people that help each other. We all have an interest in measurement theory for psychology and psychometrics. Through *discussions*, *solidarity*, and *openness*, we are boosting psychological science by improving measurement.

<div class="headers">
<h1>Join our discussion</h1>
</div>

```{r}
# teste
as_card(group_name = "Reading list",
        event_name = "Here you will find papers suggested by our community and you may add a suggestion yourself.",
        img_src = "images/google_sheets.svg",
        link = 'https://docs.google.com/spreadsheets/d/1VUtka6tC1bZucqsJ-8pvOM78azqjYyrIS4Dt3tCtrdg/edit#gid=0'
        )
```

```{r}
as_card(group_name = "Sign up",
        event_name = "If you want to take part in our live sessions, follow this link to fill the interest form.",
        img_src = "images/google_forms.svg",
        link = 'https://forms.gle/LhhBVLEX5C9Ybnta8'
        )
```

<div class="headers">
<h1>Community</h1>
</div>

```{r, layout="l-screen-inset"}
library(leaflet)
map_data <- readr::read_csv("assets/map_data.csv")
# calculate center point for setting zoom
bbox <- ggmap::make_bbox(map_data$longitude, map_data$latitude)
lon <- sum(bbox[c(1, 3)]) / 2
lat <- sum(bbox[c(2, 4)]) / 2

map_data %>% 
        leaflet() %>%
        setView(lon, lat, zoom =1) %>% 
        addTiles() %>% 
        addMarkers(lng = ~longitude, lat = ~latitude, 
                popup = paste0(
                '<b>Contry:</b> ',map_data$university, '<br>',
                '<b>Participants:</b> ', map_data$n, '<br>'
                ),
                clusterOptions = markerClusterOptions()
        )
```


<div class="headers">
<h1>Meetings calendar</h1>
</div>

```{r}
toastui::calendar()

```


<div class="headers">
<h1>Join our Slack channel</h1>
</div>

Link to the channel

<div class="headers">
<h1>About us</h1>
</div>

```{r}
plot(hist(mtcars$disp))
```
