---
title: "MEASURING PSYCHOLOGY"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, warning=FALSE, echo=FALSE}
source(here::here("R", "functions.R"))
```


**Measuring Psychology** is a global community and study group of aspiring and current students, professors, and interested people that help each other. We all have an interest in measurement theory for psychology and psychometrics. Through *discussions*, *solidarity*, and *openness*, we are boosting psychological science by improving measurement.

<div class="headers">
<h1>Join our discussion</h1>
</div>

```{r reading list}
as_card(group_name = "Reading list",
        event_name = "A list of papers suggested by our community. You may add a suggestion yourself.",
        img_src = "images/google_sheets.svg",
        link = 'https://docs.google.com/spreadsheets/d/1VUtka6tC1bZucqsJ-8pvOM78azqjYyrIS4Dt3tCtrdg/edit#gid=0'
        )
```

```{r sign up form}
as_card(group_name = "Sign up",
        event_name = "If you want to join our live meetings, follow this link to fill the interest form.",
        img_src = "images/google_forms.svg",
        link = 'https://forms.gle/LhhBVLEX5C9Ybnta8'
        )
```

<div class="headers">
<h1>Community</h1>
</div>

As you can see on the map, we have a growing community from almost all parts of the world, with different backgrounds. For instance, we are: 

  a. both from academia and industry;  
  b. from undergraduate students to Ph.D.’s;  
  c. from psychology, education, statistics, mathematics, and many more.
  
We all have an important interest, to improve our area of research by learning and applying measurement theory and psychometrics in our studies. Most importantly, we are an open-arms community, built to have a safe environment to study together, exchange ideas, and collaborate. Please, read the “About” page to see our code of conduct.

```{r map, layout="l-screen-inset"}
library(leaflet)
map_data <- readr::read_csv("assets/map_data.csv")
# calculate center point for setting zoom
bbox <- ggmap::make_bbox(map_data$longitude, map_data$latitude)
lon <- sum(bbox[c(1, 3)]) / 2
lat <- sum(bbox[c(2, 4)]) / 2

map_data %>% 
        leaflet() %>%
        setView(lon, lat, zoom =2) %>% 
        addTiles() %>% 
        addMarkers(lng = ~longitude, lat = ~latitude, 
                popup = paste0(
                '<b>Affiliation:</b> ',map_data$university, '<br>',
                '<b>Participants:</b> ', map_data$n, '<br>'
                ),
                clusterOptions = markerClusterOptions()
        )
```


<div class="headers">
<h1>Meetings calendar</h1>
</div>

To be defined in January.

```{r}
toastui::calendar()

```


<div class="headers">
<h1>Join our Slack channel</h1>
</div>

If you are interested in participating in this community, please join our slack group! You can send an email to rafavsbastos@gmail.com and marwinbr@gmail.com, and we will send you an invitation.

<div class="headers">
<h1>About us</h1>
</div>


:::::::::::::: {.columns}
::: {.column width="45%"}

```{r }
desc_rafael <- "Rafael Bastos is a Master's student in Psychology in the field of construction, validation, and standardization of instruments at São Francisco University (Brazil). Works mainly on the following subjects: psychometrics, statistics, and quantitative methods."

profile_card(img_src = "images/rafael.jpg", name = "Rafael Bastos", title="Founder and Administrator", 
             description = desc_rafael, 
             email="mailto:rafavsbastos@gmail.com",
             website="https://rafavsbastos.medium.com/",
             twitter="https://twitter.com/rafavsbastos",
             linkedin="https://www.linkedin.com/in/rafael-valdece-sousa-bastos/")

``` 

:::
::: {.column width="10%" }
\
<!-- an empty Div (with a white space), serving as
a column separator -->
:::
::: {.column width="45%"}

```{r }
desc_marwin <- "Marwin Carmo is a Master's student in Psychiatry at University of São Paulo (Brazil). Works mainly on the following subjects: construction and validation of psychological instruments, mental health, and social psychology."

profile_card(img_src = "images/marwin.jpg", name = "Marwin Carmo", title = "Founder and Administrator",
             description = desc_marwin, 
             email="mailto:marwin@usp.br",
             website="marwincarmo.github.io",
             twitter="https://twitter.com/marwincarmo",
             linkedin="https://www.linkedin.com/in/marwin-carmo/")
``` 

:::
::::::::::::::

