---
title: "MEASURING PSYCHOLOGY"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, warning=FALSE, echo=FALSE}
source(here::here("R", "functions.R"))
```


**Measuring Psychology** is a global community and study group of aspiring and current students, professors, and interested people that help each other. We all have an interest in measurement theory for psychology and psychometrics. Through *discussions*, *solidarity*, and *openness*, we are boosting psychological science by improving measurement.

<div class="headers">
<h1>Join our discussion</h1>
</div>

```{r reading list}
as_card(group_name = "Reading list",
        event_name = "A list of papers suggested by our community.\\n",
        img_src = "images/google_sheets.svg",
        link = 'https://docs.google.com/spreadsheets/d/1TePQGZySKnxl4N48EBgCYNvXzML98W3DvcudhRJ3AvY/edit?usp=sharing'
        )
```

```{r sign up form}
as_card(group_name = "Sign up",
        event_name = "If you want to join our live meetings, follow this link to fill the registration form.",
        img_src = "images/google_forms.svg",
        link = 'https://forms.gle/NVkAWxrzNqnNqsp17'
        )
```

<div class="headers">
<h1>Community</h1>
</div>

As you can see on the map, we have a growing community from almost all parts of the world, with different backgrounds. For instance, we are: 

  a. both from academia and industry;  
  b. from undergraduate students to Ph.D.’s;  
  c. from psychology, education, statistics, mathematics, and many more.
  
We all have an important interest, to improve our area of research by learning and applying measurement theory and psychometrics in our studies. Most importantly, we are an open-arms community, built to have a safe environment to study together, exchange ideas, and collaborate. Please, consider reading our [code of conduct](coc.html).

```{r map, layout="l-screen-inset"}
library(leaflet)
map_data <- readr::read_csv("assets/map_data_fixed.csv")
# calculate center point for setting zoom
bbox <- ggmap::make_bbox(map_data$longitude, map_data$latitude)
lon <- sum(bbox[c(1, 3)]) / 2
lat <- sum(bbox[c(2, 4)]) / 2

map_data %>% 
        leaflet() %>%
        setView(lon, lat, zoom =2) %>% 
        addTiles() %>% 
        addMarkers(lng = ~longitude, lat = ~latitude, 
                popup = paste0(
                '<b>Affiliation:</b> ',map_data$university, '<br>',
                '<b>Participants:</b> ', map_data$n, '<br>'
                ),
                clusterOptions = markerClusterOptions()
        )
```


<div class="headers">
<h1>Meetings calendar</h1>
</div>


```{r}
toastui::calendar()

```


<div class="headers">
<h1>Join our Slack channel</h1>
</div>

If you are interested in participating in this community, please fill the registration form. We'll send an invitation to the Slack workspace for every registered participant.

<div class="headers">
<h1>About us</h1>
</div>


:::::::::::::: {.columns}
::: {.wrap width="50%"}


```{r }
desc_rafael <- "Rafael Bastos is a Master's student in Psychology in the field of construction, validation, and standardization of instruments at São Francisco University (Brazil). Works mainly on the following subjects: psychometrics, statistics, and quantitative methods."

profile_card(img_src = "images/rafael.jpg", name = "Rafael Bastos", title="Founder and Administrator", 
             description = desc_rafael, 
             email="mailto:rafavsbastos@gmail.com",
             website="https://rafavsbastos.medium.com/",
             twitter="https://twitter.com/rafavsbastos",
             linkedin="https://www.linkedin.com/in/rafael-valdece-sousa-bastos/")

``` 

:::
::: {.wrap width="50%"}

```{r }
desc_marwin <- "Marwin Carmo is a Master's student in Psychiatry at University of São Paulo (Brazil). Interested in:
sleep medicine, psychometrics, quantitative methods, open science, and R programming."

profile_card(img_src = "images/marwin.jpg", name = "Marwin Carmo", title = "Founder and Administrator",
             description = desc_marwin, 
             email="mailto:marwin@usp.br",
             website="https://marwincarmo.github.io/",
             twitter="https://twitter.com/marwincarmo",
             linkedin="https://www.linkedin.com/in/marwin-carmo/")
``` 

:::
::::::::::::::

